### 2014-12-27 mcmc.tex
variance

What are your best options for the ``uncertainty'' or ``limits'' on this parameter?
The only simple integral-based options are posterior quantiles.
That is, the ``one-sigma'' error bar can be the size of the central (or smallest%
  \note{HOGG shizzle about choosing quantiles}) interval of the parameter
  that contains 68 percent of the posterior samples.
The ``two-sigma'' error bar would be the same but for the 95-percent interval.
Again, these limits can be estimated%
  \note{One amusing thing about samplings,
  which are so beloved of us probabilistic (Bayesian) reasoners,
  is that anything we \emph{do} with a sampling,
  like estimate an integral or a quantile,
  is just an old-school frequentist estimator.
  A frequentist estimator of a Bayesian quantity, to be sure, but a frequentist estimator nonetheless.}
  by ordering the $q(\pars_k)$ values,
  and finding the $\pars$ values such that some fraction (0.68 or 0.95)y
  of the samples lie between them.
Again, to form these limits, $q(\pars)$ must be a scalar function (so sorting is well defined).

>>>>

What are your best options for the ``uncertainty'' or ``limits'' on this parameter?
The only simple integral-based options are either variances or else posterior quantiles.
We usually use quantiles.
That is, the ``one-sigma'' error bar can be taken to be the half-size of the central (or smallest%
  \note{HOGG shizzle about choosing quantiles}) interval of the parameter
  that contains 68 percent of the posterior samples.
The ``two-sigma'' error bar would be the same but for the 95-percent interval.
Again, these limits can be estimated%
  \note{One amusing thing about samplings,
  which are so beloved of us probabilistic (Bayesian) reasoners,
  is that anything we \emph{do} with a sampling,
  like estimate an integral or a quantile,
  is just an old-school frequentist estimator.
  A frequentist estimator of a Bayesian quantity, to be sure, but a frequentist estimator nonetheless.}
  by ordering the $q(\pars_k)$ values,
  and finding the $\pars$ values such that some fraction (0.68 or 0.95)
  of the samples lie between them.
Again, to form these limits, $q(\pars)$ must be a scalar function (so sorting is well defined).
